Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-23 cordillera-cycle.tex
Add latex2rtf header.
Add one note about deglaciation plot colours.

% My commands
\def\idea#1{\textcolor[rgb]{0,0.5,0}{\textbf{[IDEA: #1]}}}
\def\note#1{\textcolor[rgb]{0,0,0.5}{\textbf{[NOTE: #1]}}}
\def\todo#1{\textcolor[rgb]{0.5,0,0}{\textbf{[TODO: #1]}}}
\def\aref{\textcolor[rgb]{0.5,0,0}{\textbf{[REF]}}}
\def\citep#1{}
\def\citet#1{}

@@

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,\unit{kyr}.
           Aside the location of present-day ice caps, note the persistence of
           a central ice dome over the Skeena mountains during most of the
           simulation. On the other hand, the maximal extent of the ice sheet
           corresponds to short durations of ice cover along most of the margin.}
  \label{fig:duration}
\end{figure}

>>>>

% My commands
\newcommand{\idea}[1]{\textbf{[IDEA: #1]}}
\newcommand{\note}[1]{\textbf{[NOTE: #1]}}
\newcommand{\todo}[1]{\textbf{[TODO: #1]}}
\newcommand{\aref}[0]{\textbf{[REF]}}
\def\citep#1{}
\def\citet#1{}

@@

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,\unit{kyr}.
           Aside the location of present-day ice caps, note the persistence of
           a central ice dome over the Skeena mountains during most of the
           simulation. On the other hand, the maximal extent of the ice sheet
           corresponds to short durations of ice cover along most of the
           margin.
           \note{I am trying to improve the readability of low ice cover
           duration values on this figure.}}
  \label{fig:duration}
\end{figure}
